Age-related changes in plant growth and traits

### 2015-04-01 leaflifespan.Rmd
Transfer extra calculations into accesrory costs
Rename age2 to age_exact

harvest <- filter(HarvestData, use_status=="use" & segment==1 & start_end=="end") %>%
  select(species,individual,age,age2,height,total_leaf_weight,site)

investment <- ReproductionAllocation_all
investment$age2 <- investment$age
investment$age <- round(investment$age, digits=1)

accessory <- AccessoryCosts_all
accessory$age2 <- accessory$age
accessory$age <- round(accessory$age, digits=1)
#accessory$PerAccessory <- {
#  select(accessory, Total >0,
#  1 - (accessory$Prop/accessory$Total)
#}

#accessory$PerPropagule = 1 - accessory$PerAccessory

@@

#adding investment and accessory costs data to leafLifespan dataframe to create a dataframe with all individual level data
SummaryInd <- merge(leafLifespan, select(investment, -species, -age), by="individual")
SummaryInd <- merge(SummaryInd, select(accessory, -species, -age, -age2), by="individual")
SummaryInd <- merge(SummaryInd, select(harvest, -species, -age, -age2), by="individual")

>>>>

harvest <- filter(HarvestData, use_status=="use" & segment==1 & start_end=="end") %>%
  select(species,individual,age,height,total_leaf_weight,site)

investment <- ReproductionAllocation_all
accessory <- AccessoryCosts_all

@@

#adding investment and accessory costs data to leafLifespan dataframe to create a dataframe with all individual level data
SummaryInd <- merge(leafLifespan, select(investment, -species, -age), by="individual")
SummaryInd <- merge(SummaryInd, select(accessory, -species, -age), by="individual")
SummaryInd <- merge(SummaryInd, select(harvest, -species, -age), by="individual")

### 2015-04-01 talk.Rmd
creating separate R scripts for analysis of different variables
Rename age2 to age_exact

harvest <- filter(HarvestData, use_status=="use" & segment==1 & start_end=="end") %>%
  select(species,individual,age,age2,height,total_leaf_weight,site)

investment <- ReproductionAllocation_all
investment$age2 <- investment$age
investment$age <- round(investment$age, digits=1)

accessory <- AccessoryCosts_all
accessory$age2 <- accessory$age
accessory$age <- round(accessory$age, digits=1)
#accessory$PerAccessory <- {
#  select(accessory, Total >0,
#  1 - (accessory$Prop/accessory$Total)
#}

#accessory$PerPropagule = 1 - accessory$PerAccessory

>>>>

harvest <- filter(HarvestData, use_status=="use" & segment==1 & start_end=="end") %>%
  select(species,individual,age,height,total_leaf_weight,site)

investment <- ReproductionAllocation_all

accessory <- AccessoryCosts_all
